Priors

### 2023-06-30 reports/county_figures.Rmd
figures

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,cache=TRUE, fig.width=10, fig.height=7)

library(tidyverse)
library(targets)
library(here)
library(latex2exp)
library(kableExtra)
library(scales)
library(cowplot)
```

@@

@@

@@

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"

@@

w_data <- wjoined %>% 
  select(-date) %>%
  distinct() %>%
  filter(fips %in% counties_with_waste) %>%
  filter(!is.na(mean_conc)) %>%
  group_by(fips, version) %>%
  mutate(mean_conc_std = mean_conc/ max(mean_conc),
         exp_cases_median_std = exp_cases_median / max(exp_cases_median),
         exp_cases_lb_std = exp_cases_lb /max(exp_cases_median),
         exp_cases_ub_std = exp_cases_ub / max(exp_cases_median),
         infections_std  = infections/max(infections),
         positive_std = positive/max(positive)) %>%
  ungroup()

@@

@@

covidestim_correlations <- w_data %>%
  filter(version=="v1") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(mean_conc_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

w_data %>%
  filter(version=="v1") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County)",
       y = "Wastewater Concentrations\n(Standardized by County)",
       title = "Correlations Between Wastewater Concentrations\nand Covidestim Estimates")

pb_correlations <- w_data %>%
  filter(version=="v1") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(positive_std,mean_conc_std,
                              use = "complete.obs")) %>%
  mutate(x=1.8,
         y=.1)

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Emp. Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$",
               "$\\beta$ Centered at Emp. Value"
               )

@@

pltlist <- w_data %>%
  mutate(name = gsub("County, MA", "", name)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  # filter(version %in% c("v1","v3")) %>%
  filter(version=="v1") %>%
  filter(biweek>=6) %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate=max(date)) %>%
  ungroup() %>% 
  group_by(name) %>%
  group_split() %>%
  map(~ {

@@

cowplot::plot_grid(legend, grid, nrow=2, rel_heights=c(.05,.95))

@@

 w_data_std <- w_data %>%
  group_by(name, version) %>%
  mutate(exp_cases_lb = exp_cases_lb /max(exp_cases_median),
         exp_cases_ub = exp_cases_ub /max(exp_cases_median),
         exp_cases_median = exp_cases_median / max(exp_cases_median),
         mean_conc=mean_conc/max(mean_conc),
         infections=infections/max(infections)) %>%
  mutate(name = gsub("County, MA", "", name)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  filter(version %in% c("v1","v3")) %>%
  filter(biweek>=6) %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate=max(date)) %>%
  ungroup()

@@

@@

@@

@@

covidestim_correlations <- w_data %>%
  filter(version=="v1") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(mean_conc_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

w_data %>%
  filter(version=="v1") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County by County)",
       y = "Wastewater Concentrations\n(Standardized by County by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

pb_correlations <- w_data %>%
  filter(version=="v1") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(positive_std,mean_conc_std,
                              use = "complete.obs")) %>%
  mutate(x=1.8,
         y=.1)

@@

@@

w_data%>%
  mutate(name = gsub("County, MA", "", name)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  filter(version %in% c("v1","v3")) %>%
  filter(biweek>=6) %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate=max(date)) %>%
  ungroup() %>% 
 #   filter(fips == county_fips  & date >= begin_date & date <= end_date) %>%
    ggplot() +
      geom_ribbon(aes(x = date, 
                 ymin = exp_cases_lb_std,
                 ymax = exp_cases_ub_std,
                 fill = vlabel),
                 alpha = .5) +
      geom_line(data = waste_df,
                aes(x = date, y =mean_conc_std, 
                    color = 'Wastewater Effective Concentrations'),
               # color = "#DB4048",
                size = 1.1) +
      geom_linerange(aes(xmin = mindate, 
                         xmax = maxdate, 
                         y = infections_std,
                         color = 'Covidestim Infection Estimates')) + 
      geom_point(data = waste_df,
                aes(x = date, y =mean_conc_std ),
                color = "#DB4048",
                alpha = .5,
                size = 1.2) +
      facet_grid(name~vlabel, 
                 labeller=labeller(vlabel =as_labeller(
                   TeX, default=label_parsed))) +
      scale_fill_manual(values = pal, labels = c('','','',''), 
                        name = "Probabilistic Bias Intervals") +
      theme_bw() +
     theme_c() +
      labs(y = "Value (Standardized by County by County)",
           title = "",
           x= "") +
      scale_x_date(date_labels = "%b %Y") +
    scale_color_manual(
      name = '', 
      values = c(
        'Covidestim Infection Estimates' = 'darkblue',
        'Wastewater Effective Concentrations' = '#DB4048')) +
    guides(color = guide_legend(override.aes = list(size = 12,
                                                    linewidth=3)),
           fill = guide_legend(override.aes =list(size = 6)))

@@

```{r, fig.height=10, fig.width=10}

@@

covidestim_correlations <- w_data %>%
  filter(version=="v1") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(mean_conc_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

w_data %>%
  filter(version=="v1") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County)",
       y = "Wastewater Concentrations\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

pb_correlations <- w_data %>%
  filter(version=="v1") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(positive_std,mean_conc_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

@@

```{r, fig.width=11, fig.height=8}

@@

county_dat %>%
  filter(version=="v1")  %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_wrap(~name, scales="free_y", ncol=3) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

@@

county_dat %>%
  filter(version=="v1")  %>%
  #filter(grepl("Nan",name)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb/positive,
             ymax = exp_cases_ub/positive),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   # geom_linerange(aes(xmin = mindate,
   #                    xmax=maxdate,
   #                    y = positive,
   #                    color = 'obs')) +
  facet_wrap(~name,ncol=3) +
 # facet_grid(name~vlabel, 
 #                 labeller=labeller(vlabel =as_labeller(
 #                   TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top") +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Ratio of Estimated to Observed Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

############################################
# POSITIVE TESTS AND TEST POSITIVITY
############################################
pltlist <- county_dat %>%filter(version=="v1") %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  mutate(adj = (1/max(testpos)) * max(positive)) %>%
  group_split() %>%
  map(~ {
    adj <-unique(.x$adj)
    .x %>%
      ggplot(aes(x=date))+
    geom_line(aes(y=positive, color = 'Positive Tests')) +
      geom_point(aes(y=positive, color = 'Positive Tests'),
              alpha=.5,
              size=.8) +
    geom_line(aes(y=testpos*adj, color='Test Positivity'),
              linetype=2) +
      geom_point(aes(y=testpos*adj, color='Test Positivity'),
              alpha=.5,
              size=.8) +
    #scale_linetype_discrete(breaks = c(1,1,2)) +
    scale_color_manual(values=c(
                                "Positive Tests"= "#279143",
                                "Test Positivity"= '#E38E4F')) +
    guides(color = guide_legend(override.aes = list(linetype = c(1,2),
                                                    linewidth=c(2,2)))) +
    theme_c() +
    theme(axis.title = element_text(size=10),
          axis.text =element_text(size=9),
          legend.position="none") +
    scale_y_continuous(labels=comma, sec.axis = sec_axis(~./adj , name = 'Test Positivity')) +
    labs(color ='',
         y="Positive Tests",
         x= "Date") +
      facet_wrap(~name)

@@

#####################################
# TOTAL TESTS AND POSITIVE TESTS
#####################################
pltlist <- county_dat %>%filter(version=="v1") %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  mutate(adj = (1/max(total)) * max(positive)) %>%
  group_split() %>%
  map(~ {
    adj <-unique(.x$adj)
    .x %>%
      ggplot(aes(x=date))+
    geom_line(aes(y=positive, color = 'Positive Tests')) +
      geom_point(aes(y=positive, color = 'Positive Tests'),
              alpha=.5,
              size=.8) +
    geom_line(aes(y=total*adj, color='Total Tests'),
              linetype=2) +
      geom_point(aes(y=total*adj, color='Total Tests'),
              alpha=.5,
              size=.8) +
    #scale_linetype_discrete(breaks = c(1,1,2)) +
    scale_color_manual(values=c(
                                "Positive Tests"= "#279143",
                                "Total Tests"= '#E38E4F')) +
    guides(color = guide_legend(override.aes = list(linetype = c(1,2)))) +
    theme_c() +
    theme(axis.title = element_text(size=11),
          axis.text =element_text(size=8),
          legend.position="none") +
    scale_y_continuous(labels=label_scientific(), 
                       n.breaks=4,
                       sec.axis = sec_axis(~./adj ,
                                           name = 'Total Tests',
                                           labels=label_scientific())) +
    labs(color ='',
         y="Positive Tests",
         x= "Date") +
      facet_wrap(~name)
})

@@

county_dat %>%
  filter(version=="v1") %>%
  filter(!grepl("Nantucket",name)) %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  arrange(biweek) %>%
  mutate(pct_change_positive = (positive - lag(positive, 1))/lag(positive, 1),
         pct_change_total = (total - lag(total, 1))/lag(total, 1)) %>%

@@

##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,cache=FALSE, fig.width=10, fig.height=7)

library(tidyverse)
library(targets)
library(here)
library(latex2exp)
library(kableExtra)
library(scales)
library(cowplot)

filter_versions <- FALSE 
save_figures <- FALSE

include_other_norm <- FALSE

@@

pal <- c("red", "#10BAC5", "#1B10C5", "#EFB719", "#900C3F")

names(pal) <- c("Covidestim",
                '$P(S_1|untested)$ Centered at Survey Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

if(filter_versions) {
  county <- county %>%
    filter(version %in% c("v3", "v5", "v6", "v7")) 
}

@@

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|untested)$ Centered at Survey Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Survey Value",
         "$P(S_1|untested)$ Centered at Survey Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"

@@

@@

```{r, fig.height=10, fig.width=14}

cowplot::plot_grid(plt_wastewater_pb, plt_covidestim_pb, ncol=2,  labels="auto", label_size=19)

```{r,eval=save_figures}

ggsave(here("figures/correlations-wastewater-by-version.pdf"))

@@

covidestim_correlations <- w_data %>%
  filter(version=="v7") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(mean_conc_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County)",
       y = "Wastewater Concentrations\n(Standardized by County)",
       title = "Correlations Between Wastewater Concentrations\nand Covidestim Estimates")

pb_correlations <- w_data %>%
  filter(version=="v7") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(positive_std,mean_conc_std,
                              use = "complete.obs")) %>%
  mutate(x=1.8,
         y=.1)

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Survey Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

pltlist <- w_data %>%
  mutate(name = gsub("County, MA", "", name)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  # filter(version %in% c("v7","v3")) %>%
  filter(version=="v7") %>%
  filter(biweek>=6) %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate=max(date)) %>%
  ungroup() %>% 
  group_by(name) %>%
  group_split() %>%
  map(~ {

@@

cowplot::plot_grid(legend, grid, nrow=2, rel_heights=c(.05,.95))
```

```{r, eval=save_figures}

ggsave(here('figures/simulation-intervals-wastewater.pdf'))

@@

 w_data_std <- w_data %>%
  group_by(name, version) %>%
  mutate(exp_cases_lb = exp_cases_lb /max(exp_cases_median),
         exp_cases_ub = exp_cases_ub /max(exp_cases_median),
         exp_cases_median = exp_cases_median / max(exp_cases_median),
         mean_conc=mean_conc/max(mean_conc),
         infections=infections/max(infections)) %>%
  mutate(name = gsub("County, MA", "", name)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  filter(version %in% c("v7","v3")) %>%
  filter(biweek>=6) %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate=max(date)) %>%
  ungroup()

@@

```{r, eval=include_other_norm}

@@

```{r,eval=include_other_norm}

@@

```{r, fig.height=10, fig.width=12,eval=include_other_norm}

@@

```{r,eval=include_other_norm}

covidestim_correlations <- w_data %>%
  filter(version=="v7") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(mean_conc_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County by County)",
       y = "Wastewater Concentrations\n(Standardized by County by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

pb_correlations <- w_data %>%
  filter(version=="v7") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(positive_std,mean_conc_std,
                              use = "complete.obs")) %>%
  mutate(x=1.8,
         y=.1)

@@

```{r,fig.width=12, fig.height=15,eval=include_other_norm}

@@

w_data%>%
  mutate(name = gsub("County, MA", "", name)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  filter(version %in% c("v7","v3")) %>%
  filter(biweek>=6) %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate=max(date)) %>%
  ungroup() %>% 
 #   filter(fips == county_fips  & date >= begin_date & date <= end_date) %>%
    ggplot() +
      geom_ribbon(aes(x = date, 
                 ymin = exp_cases_lb_std,
                 ymax = exp_cases_ub_std,
                 fill = vlabel),
                 alpha = .5) +
      geom_line(data = waste_df,
                aes(x = date, y =mean_conc_std, 
                    color = 'Wastewater Effective Concentrations'),
               # color = "#DB4048",
                size = 1.1) +
      geom_linerange(aes(xmin = mindate, 
                         xmax = maxdate, 
                         y = infections_std,
                         color = 'Covidestim Infection Estimates')) + 
      geom_point(data = waste_df,
                aes(x = date, y =mean_conc_std ),
                color = "#DB4048",
                alpha = .5,
                size = 1.2) +
      facet_grid(name~vlabel, 
                 labeller=labeller(vlabel =as_labeller(
                   TeX, default=label_parsed))) +
      scale_fill_manual(values = pal, labels = c('','','',''), 
                        name = "Probabilistic Bias Intervals") +
      theme_bw() +
     theme_c() +
      labs(y = "Value (Standardized by County by County)",
           title = "",
           x= "") +
      scale_x_date(date_labels = "%b %Y") +
    scale_color_manual(
      name = '', 
      values = c(
        'Covidestim Infection Estimates' = 'darkblue',
        'Wastewater Effective Concentrations' = '#DB4048')) +
    guides(color = guide_legend(override.aes = list(size = 12,
                                                    linewidth=3)),
           fill = guide_legend(override.aes =list(size = 6)))

@@

```{r, fig.height=10, fig.width=10,eval=include_other_norm}

@@

```{r,eval=include_other_norm}

covidestim_correlations <- w_data %>%
  filter(version=="v7") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(mean_conc_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

w_data %>%
  filter(version=="v7") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized by County)",
       y = "Wastewater Concentrations\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Counts\nand Covidestim Estimates")

pb_correlations <- w_data %>%
  filter(version=="v7") %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(positive_std,mean_conc_std,
                              use = "complete.obs")) %>%
  mutate(x=1,
         y=.1)

@@

```{r, fig.width=13, fig.height=8}

@@

county_dat %>%
  filter(version=="v7")  %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_wrap(~name, scales="free_y", ncol=3) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
    axis.text.x=element_text(size=7),
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

```{r, eval=save_figures}

ggsave(here('figures/simulation-intervals-county.pdf'))

```{r,fig.width=14, fig.height=8}

@@

county_dat %>%
  filter(version=="v7")  %>%
  #filter(grepl("Nan",name)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb/positive,
             ymax = exp_cases_ub/positive),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   # geom_linerange(aes(xmin = mindate,
   #                    xmax=maxdate,
   #                    y = positive,
   #                    color = 'obs')) +
  facet_wrap(~name,ncol=3) +
 # facet_grid(name~vlabel, 
 #                 labeller=labeller(vlabel =as_labeller(
 #                   TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top") +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Ratio of Estimated to Observed Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

############################################
# POSITIVE TESTS AND TEST POSITIVITY
############################################
pltlist <- county_dat %>%filter(version=="v7") %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  mutate(adj = (1/max(testpos)) * max(positive)) %>%
  group_split() %>%
  map(~ {
    adj <-unique(.x$adj)
    .x %>%
      ggplot(aes(x=date))+
    geom_line(aes(y=positive, color = 'Positive Tests')) +
      geom_point(aes(y=positive, color = 'Positive Tests'),
              alpha=.5,
              size=.8) +
    geom_line(aes(y=testpos*adj, color='Test Positivity'),
              linetype=2) +
      geom_point(aes(y=testpos*adj, color='Test Positivity'),
              alpha=.5,
              size=.8) +
    #scale_linetype_discrete(breaks = c(1,1,2)) +
    scale_color_manual(values=c(
                                "Positive Tests"= "#279143",
                                "Test Positivity"= '#E38E4F')) +
    guides(color = guide_legend(override.aes = list(linetype = c(1,2),
                                                    linewidth=c(2,2)))) +
    theme_c() +
    theme(axis.title = element_text(size=10),
          axis.text =element_text(size=9),
          legend.position="none") +
    scale_y_continuous(labels=comma, sec.axis = sec_axis(~./adj , name = 'Test Positivity')) +
    labs(color ='',
         y="Positive Tests",
         x= "Date") +
      facet_wrap(~name)

@@

#####################################
# TOTAL TESTS AND POSITIVE TESTS
#####################################
pltlist <- county_dat %>%filter(version=="v7") %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  mutate(adj = (1/max(total)) * max(positive)) %>%
  group_split() %>%
  map(~ {
    adj <-unique(.x$adj)
    .x %>%
      ggplot(aes(x=date))+
    geom_line(aes(y=positive, color = 'Positive Tests')) +
      geom_point(aes(y=positive, color = 'Positive Tests'),
              alpha=.5,
              size=.8) +
    geom_line(aes(y=total*adj, color='Total Tests'),
              linetype=2) +
      geom_point(aes(y=total*adj, color='Total Tests'),
              alpha=.5,
              size=.8) +
    #scale_linetype_discrete(breaks = c(1,1,2)) +
    scale_color_manual(values=c(
                                "Positive Tests"= "#279143",
                                "Total Tests"= '#E38E4F')) +
    guides(color = guide_legend(override.aes = list(linetype = c(1,2)))) +
    theme_c() +
    theme(axis.title = element_text(size=11),
          axis.text =element_text(size=8),
          legend.position="none") +
    scale_y_continuous(labels=label_scientific(), 
                       n.breaks=4,
                       sec.axis = sec_axis(~./adj ,
                                           name = 'Total Tests',
                                           labels=label_scientific())) +
    labs(color ='',
         y="Positive Tests",
         x= "Date") +
      facet_wrap(~name)
})

@@

county_dat %>%
  filter(version=="v7") %>%
  filter(!grepl("Nantucket",name)) %>%
    mutate(testpos = positive/total) %>%
  group_by(across(-date)) %>%
  summarize(date=min(date) + days(7)) %>%
  group_by(fips) %>%
  arrange(biweek) %>%
  mutate(pct_change_positive = (positive - lag(positive, 1))/lag(positive, 1),
         pct_change_total = (total - lag(total, 1))/lag(total, 1)) %>%

@@

##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Survey Value") %>%
  group_by(name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))

### 2023-06-30 reports/priors.Rmd
figures

beta_shape = get_shape(ctis_smoothed,
                             option="beta",
                       quiet=TRUE)

@@

s_untested_shape = get_shape(ctis_smoothed,
                             option="s_untested",
                       quiet=TRUE)

@@

>>>>

beta_shape = get_shape(ctis_smoothed,
                             option="beta",
                       quiet=FALSE)

@@

s_untested_shape = get_shape(ctis_smoothed,
                             option="s_untested",
                       quiet=FALSE)

@@

```{r,eval=FALSE}

ctis_smoothed <- tar_read(ctis_smoothed,
                          store=here("_targets"))

ctis_smoothed %>% left_join(dates) %>%
  group_by(biweek,state) %>%
  summarize(beta_est=mean(beta_est,na.rm=TRUE)) %>%
  ungroup() %>%
  summarize(q1 = quantile(beta_est,.025, na.rm=TRUE),
                median = median(beta_est, na.rm=TRUE),
                q2 = quantile(beta_est,.975, na.rm=TRUE),
                sd=sd(beta_est,na.rm=TRUE))

ctis_smoothed %>%
      summarize(q1 = quantile(
        beta_estimate_spline_smoothed,.025, na.rm=TRUE),
        median = median(beta_estimate_spline_smoothed, na.rm=TRUE),
        q2 = quantile(beta_estimate_spline_smoothed,.975, na.rm=TRUE),
        sd=sd(beta_estimate_spline_smoothed,na.rm=TRUE))
